% This is a polished LaTeX document for an Independent Contractor Agreement.
%
% Revision 9 (Consolidation):
% 1. Moved the Disclaimer from the Addendum to the top of the document.
% 2. Deleted the redundant Section 7 (Intellectual Property Rights).
% 3. Deleted the entire Section 11 (Addendum).
% 4. Promoted the content from the Addendum into the main body.
% 5. Created a new Section 6 (Client Materials and Responsibilities)
%    from item 1 of the old Addendum.
% 6. Created a new Section 7 (Intellectual Property Rights) from
%    items 2 and 3 of the old Addendum, and re-incorporated the
%    portfolio clause.
% 7. Renumbered all subsequent sections.
% 8. Populated Contractor name (Jaehoon Song) in the signature block
%    and party definition for clarity.

\documentclass{article}

% -------------------------------------------------------------------
% \ PACKAGES
% -------------------------------------------------------------------

% Encoding
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Language
\usepackage[english]{babel}

% Page Layout
\usepackage[margin=1in]{geometry} % Standard 1-inch margins
\usepackage{parskip}          % Space between paragraphs, no indent
\setlength{\parskip}{1em}
\setlength{\parindent}{0pt}

% Headers & Footers
\usepackage{fancyhdr}
\pagestyle{plain} % Use "plain" for page numbers at the bottom
\fancyhf{} % Clear all header and footer fields
\fancyfoot[C]{\thepage} % Center page number in footer

% Hyperlinks (for PDF)
\usepackage{hyperref}

% For \begin{enumerate}
\usepackage{enumitem}

% -------------------------------------------------------------------
% \ DOCUMENT START
% -------------------------------------------------------------------
\begin{document}


% --- TITLE ---
\begin{center}
  \Large\textbf{Independent Contractor Agreement}
\end{center}
\vspace{1.0em}

% --- DISCLAIMER ---
\noindent\textit{\textbf{Disclaimer}: This document memorializes 
the parties' understanding but does not constitute legal advice. 
Each party should consult its own counsel regarding rights and obligations.}
\vspace{1.5em}

% --- PARTIES ---
This Independent Contractor Agreement (the ``Agreement'') is entered into as of 
\today{} (the ``Effective Date''), by and between the undersigned client (the ``Client'') 
and the undersigned copywriter (the ``Contractor''). The Agreement confirms 
the Contractor's engagement for the following project initiative and provides 
written support for the Client's project expense.

\vspace{1.0em}

\noindent
\begin{minipage}[t]{0.28\linewidth}
  \textbf{Client:}
\end{minipage}
\begin{minipage}[t]{0.68\linewidth}
  \rule{\linewidth}{0.4pt} \\
  (Client's Name)
\end{minipage}

\vspace{1.0em}

\noindent
\begin{minipage}[t]{0.28\linewidth}
  \textbf{Contractor:}
\end{minipage}
\begin{minipage}[t]{0.68\linewidth}
  \rule{\linewidth}{0.4pt} \\
  (Contractor's Name)
\end{minipage}

\vspace{1.0em}


\noindent
\begin{minipage}[t]{0.28\linewidth}
  \textbf{Project Reference:}
\end{minipage}
\begin{minipage}[t]{0.68\linewidth}
  \rule{\linewidth}{0.4pt} \\
  (Project Reference)
\end{minipage}

\vspace{1.0em}

% -------------------------------------------------------------------
% \ AGREEMENT SECTIONS
% -------------------------------------------------------------------
\subsection*{Engagement and Purpose}
Client engages Contractor to provide a limited scope of web design and front-end development services for the JS Law Group website. The parties intend that this Agreement document the scope, deliverables, payment, and responsibilities so the Client may maintain defensible accounting and tax records for the engagement.

\subsection*{Scope of Services}
Contractor will perform the services described in the \textbf{System Design Documentation} attached as \textbf{Exhibit A} (collectively, the ``Specification''). This includes creating responsive layouts, applying UI design updates, refining user interface copy provided by Client, and implementing front-end interactions consistent with the Specification. Task sequencing may evolve as Client clarifies priorities, provided changes are confirmed in writing (including email).

\subsection*{Term and Schedule}
The anticipated project period is \textbf{three (3) weeks} from the Effective Date. The parties will collaborate in good faith to remove blockers promptly so milestones can be completed within this period. Any extension or acceleration must be mutually agreed via email or signed addendum.

\subsection*{Deliverables and Acceptance}
Deliverables include all updated source files (HTML, CSS, JavaScript, JSON), component assets, and configuration files committed to Client's repository or transmitted through a secure channel. Contractor will provide reasonable implementation notes upon handoff. Client will review deliverables within five (5) business days and notify Contractor of any material deficiencies tied to the Specification. If no notice is provided within that period, the deliverables are deemed accepted. Contractor will address reported deficiencies within a reasonable time at no extra charge when they relate to the agreed scope.

\subsection*{Compensation, Invoicing, and Documentation}
\begin{enumerate}
  \item \textbf{Base Fee.} Client shall pay Contractor a fixed project fee of \textbf{\$2{,}000 USD}. Fifty percent (50\%, \$1{,}000) is due at project kickoff and the remaining fifty percent (50\%, \$1{,}000) is due upon Client's acceptance of the final deliverables.
  \item \textbf{Variable Scope Allowance.} If Client requests additional work beyond the Specification (for example, extra locales or new page sections), the parties may authorize up to an additional thirty percent (30\%) of the base fee (maximum \$600). Any such work requires written approval describing the added scope; invoices will include supporting notes and/or time detail.
  \item \textbf{Invoices and Payment.} Contractor will issue electronic invoices for each installment. Client shall remit payment within ten (10) calendar days of invoice receipt via the agreed payment method. Past-due balances may pause services until payment is received.
  \item \textbf{Tax Forms and Records.} Contractor will provide a completed IRS Form W-9 and any other information reasonably required for Client's tax compliance. Client anticipates issuing Form 1099-NEC if total payments meet the applicable threshold. Each party agrees to retain copies of this Agreement, invoices, W-9, and proof of payment for no less than four (4) years.
\end{enumerate}

\subsection*{Independent Contractor Status}
Contractor performs the services as an independent contractor and not as an employee, partner, fiduciary, or agent of Client. Contractor controls the manner, method, timing, and location of work, may perform services for other clients, and is solely responsible for all taxes, insurance, licenses, benefits, and equipment associated with the services. Nothing in this Agreement creates an employment relationship.

\subsection*{Client Materials and Responsibilities}
\begin{enumerate}
  \item \textbf{Provision of Assets.} Client agrees to provide Contractor, in a timely manner, all necessary assets (``Client Materials'') required for the completion of the Services. This includes, but is not limited to, all logos, branding guidelines, written text content, photographs, and other media.
  \item \textbf{Permissions.} Client represents and warrants that it owns all rights, title, and interest in the Client Materials or has secured the necessary licenses and permissions to use them for the project.
  \item \textbf{Indemnity.} Client agrees to indemnify and hold harmless Contractor from any and all claims, damages, or legal costs arising from the Contractor's use of the Client Materials as directed by the Client.
\end{enumerate}

\subsection*{Intellectual Property Rights}
\begin{enumerate}
  \item \textbf{Work Product.} "Work Product" shall mean all deliverables, source code (HTML, CSS, JavaScript, etc.), designs, graphics, and other materials created by the Contractor *specifically for this project* and as part of the project's defined scope.
  \item \textbf{Work for Hire and Assignment.} The parties agree that all Work Product shall be considered a ``work made for hire'' as defined by U.S. Copyright law. To the extent that the Work Product is not considered a ``work made for hire,'' Contractor hereby assigns all right, title, and interest in the Work Product to the Client. This assignment is contingent upon Contractor receiving full and final payment for all services rendered under this Agreement.
  \item \textbf{Pre-existing Intellectual Property.} Contractor retains all right, title, and interest in any code, tools, libraries, frameworks, techniques, and other intellectual property owned by Contractor or licensed to Contractor by a third party *prior* to this Agreement, or which are developed *outside* the scope of this project (``Developer IP''). If any Developer IP is incorporated into the final Work Product, Contractor grants Client a non-exclusive, perpetual, royalty-free license to use, copy, and modify such Developer IP *solely as part of the final website*.
  \item \textbf{Portfolio Rights.} Contractor may showcase high-level, non-confidential portfolio references from the project (e.g., screenshots or a brief description) only with Client's prior written approval.
\end{enumerate}

\subsection*{Confidential Information and Security}
All access credentials, documentation, specifications, business plans, and other non-public information shared by Client (``Confidential Information'') shall be kept confidential. Contractor will:
\begin{itemize}
  \item Use credentials solely for performing the contracted work.
  \item Store passwords and sensitive data privately (encrypted where feasible) and never disclose them publicly or to third parties without written consent.
  \item Promptly inform Client of any suspected credential compromise and assist with mitigation.
\end{itemize}
These obligations survive termination. Client will likewise protect Contractor's personal information (including the W-9) and use it only for lawful compliance.

\subsection*{Warranties and Support}
Contractor warrants that deliverables will align with the Specification (Exhibit A) and will not knowingly infringe third-party intellectual property. Contractor will remediate critical defects reported within fourteen (14) days of final delivery at no additional charge. Enhancements or new features beyond the documented scope will be estimated separately.

\subsection*{Communication and Issue Resolution}
The parties will communicate primarily via email, shared project tools, or scheduled virtual meetings. Questions and feedback will be provided within a commercially reasonable time. Any dispute will first be addressed through good-faith discussions. Both parties agree to document material concerns in writing so this Agreement and related correspondence can serve as evidence of scope, performance, and expense.

\subsection*{Termination}
Either party may terminate this Agreement with five (5) days written notice. Client shall pay Contractor for all work performed up to the termination date, including any approved variable scope. Sections on confidentiality, intellectual property, and payment obligations survive termination.

\subsection*{General Provisions}
\begin{itemize}
  \item This Agreement, including Exhibit A, represents the entire understanding between the parties regarding the services described and supersedes prior oral or written communications.
  \item Amendments must be in writing and signed (physically or electronically) by both parties.
  \item The Agreement is governed by the laws of the state in which the Client is domiciled, unless the parties agree otherwise in writing.
\end{itemize}

\vfill % Pushes the signature block to the bottom if on a new page

% --- SIGNATURE BLOCK ---
\noindent IN WITNESS WHEREOF, the parties have executed this Agreement as of the Effective Date.

\vspace{2.0em}

\noindent
\begin{minipage}[t]{0.48\linewidth}
  \textbf{CLIENT}
  \vspace{2.0em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Signature
  \vspace{1.2em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Printed Name (JS Law Group)
  \vspace{1.2em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Title
  \vspace{1.2em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Date
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\linewidth}
  \textbf{CONTRACTOR}
  \vspace{2.0em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Signature
  \vspace{1.2em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Printed Name (Jaehoon Song)
  \vspace{1.2em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Title (Contractor)
  \vspace{1.2em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Date
\end{minipage}

\end{document}
