% This is a formal LaTeX document for a Services Agreement.
%
% 1. Title changed to "Services Agreement" for a more formal tone.
% 2. A new "Independent Contractor Status" section was added
%    to cover flexibility, tools, and work schedule as requested.
% 3. Services section remains focused on the UI copy.
% 4. Sections renumbered for logical flow.

\documentclass{article}

% -------------------------------------------------------------------
% \ PACKAGES
% -------------------------------------------------------------------

% Encoding
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Language
\usepackage[english]{babel}

% Page Layout
\usepackage[margin=1in]{geometry} % Standard 1-inch margins
\usepackage{parskip}          % Space between paragraphs, no indent
\setlength{\parskip}{1em}
\setlength{\parindent}{0pt}

% Headers & Footers
\usepackage{fancyhdr}
\pagestyle{plain} % Use "plain" for page numbers at the bottom
\fancyhf{} % Clear all header and footer fields
\fancyfoot[C]{\thepage} % Center page number in footer

% Hyperlinks (for PDF)
\usepackage{hyperref}

% For \begin{enumerate}
\usepackage{enumitem}

% -------------------------------------------------------------------
% \ DOCUMENT START
% -------------------------------------------------------------------
\begin{document}

% --- TITLE ---
\begin{center}
  \Large\textbf{Copywriting Services Agreement}
\end{center}
\vspace{1.0em}

% --- PARTIES ---
This Copywriting Services Agreement (the ``Agreement'') is made as of \today{} 
(the ``Effective Date'') by and between the undersigned client (the ``Client'') 
and the undersigned copywriter (the ``Contractor''). The Agreement documents the 
Contractor's limited copywriting contribution to the \underbar{JS Law Group} 
official website project and serves as written support for the Client's related 
project expense.

\vspace{1.0em}

\noindent
\begin{minipage}[t]{0.18\linewidth}
  \textbf{Client:}
\end{minipage}
\begin{minipage}[t]{0.78\linewidth}
  \rule{\linewidth}{0.4pt} \\
  (Client's Name)
\end{minipage}

\vspace{1.0em}

\noindent
\begin{minipage}[t]{0.18\linewidth}
  \textbf{Contractor:}
\end{minipage}
\begin{minipage}[t]{0.78\linewidth}
  \rule{\linewidth}{0.4pt} \\
  (Contractor's Name) \\
  
  \vspace*{10pt} % Extra space between lines

  \rule{\linewidth}{0.4pt} \\
  (Guardian's Name, if applicable)
\end{minipage}

\vspace{1.0em}


\vspace{1.2em}

% -------------------------------------------------------------------
% \ AGREEMENT SECTIONS
% -------------------------------------------------------------------
\subsection*{Parties and Purpose}
The Client engages the Contractor solely for the \textbf{JS Law Group website} 
copywriting initiative described in this Agreement. Both parties intend that this 
document provide written confirmation of the scope, compensation, and mutual 
expectations so the Client may document and substantiate the associated business 
\underbar{expense for tax and accounting purposes}.

\subsection*{Scope of Services}
The Contractor will create, edit, and refine user-interface copy for website 
elements such as navigation, buttons, headings, and section descriptions, 
as requested by the Client. Work will be performed in \textbf{English}. 
\textbf{Any translation or multilingual support must be separately agreed} 
upon in writing. The Client will supply \underbar{technical tools}, 
\underbar{timely instructions}, \underbar{background information}, 
and \underbar{draft content}, and will \underbar{review deliverables} 
within a commercially reasonable time.

\subsection*{Term and Deliverables}
Work begins on the Effective Date and concludes when the Client accepts 
the final copy. The parties \underbar{expect completion within three (3) weeks}, 
unless they mutually agree to extend the schedule in writing or email. 
Deliverables include draft and final copy documents in editable format 
(for example, shared documents or text files) along with reasonable 
revisions requested by the Client.

\subsection*{Compensation and Tax Documentation}
This is a fixed-fee engagement totaling \textbf{\$300.00 USD}\footnote{
No additional fees, expenses, or reimbursements are contemplated unless 
agreed to in writing.}, paid in the following installments:
\begin{enumerate}[label=\alph*.]
  \item \textbf{\$150.00} due upon execution of this Agreement and delivery of the initial draft outline.
  \item \textbf{\$150.00} due within five (5) business days of the Client's written acceptance of the final deliverables.
\end{enumerate} 
Prior to the first payment, the \textbf{Contractor} 
(or the Parent/Guardian, if applicable) \underbar{will provide a completed} 
\underbar{IRS Form W-9 so the Client can maintain proper expense records}. 

Since the total compensation is below the current \$600 Form 1099-NEC 
reporting threshold, the Client does not anticipate issuing Form 1099-NEC.\footnote{
If tax laws change or the Client is otherwise required to report, the Contractor will cooperate 
by providing any additional information reasonably requested. Each party will retain this 
Agreement and payment confirmations as evidence of the transaction.}


\subsection*{Independent Contractor Relationship}
The Contractor is 
\underbar{not an employee}, \underbar{partner}, or \underbar{agent of the Client} 
and is engaged as an \textbf{independent contractor}. 
The Contractor determines how, when, and where the services are performed, 
may work for other clients, and is responsible for providing their own equipment, 
internet access, and software (e.g., Google Docs or Microsoft Word). The 
Contractor is solely responsible for all taxes, insurance, and obligations 
imposed by law on self-employed individuals. 
\underbar{The Client's oversight is limited to ensuring that the deliverables}
\underbar{meet project requirements}.

\subsection*{Communication and Cooperation}
Meetings may occur virtually or in person at mutually agreeable times. The parties will share documents electronically unless otherwise agreed. Each party will respond to questions or feedback within a reasonable timeframe in order to keep the project on track. Any requested changes to scope, deadlines, or payment must be confirmed in writing (including email) to be effective.

\subsection*{Ownership of Work Product}
All text, copy, and related materials created by the Contractor under this 
Agreement (the ``Work Product'') are considered ``work made for hire'' within 
the meaning of U.S. copyright law. Upon receipt of full payment, all rights, 
title, and interest in the Work Product automatically vest in the Client, 
who may use, modify, sublicense, or transfer the Work Product without restriction. 
The Contractor and Parent/Guardian waive any moral rights or similar claims in 
the Work Product. The \textbf{Contractor may reference the engagement in a portfolio} 
only \underbar{with the Client's written consent}.

\subsection*{Confidentiality and Records}
The Contractor will keep confidential all non-public information provided by the Client and will use such information solely to perform the services. The Client will keep the Contractor's personal information, including the Form W-9, secure and will use it only for lawful tax and recordkeeping purposes. Each party agrees to maintain copies of this Agreement, the W-9, invoices (if any), and proof of payment for at least four (4) years to substantiate the expense and this engagement.

\subsection*{Representations and Issue Resolution}
Each party represents that they have authority to enter into this Agreement. 
The Contractor represents that the Work Product will be original and will 
not knowingly infringe third-party rights. Any concern, dispute, or request 
for clarification will first be addressed through good-faith discussion 
between the Client, the Contractor, and the Parent/Guardian (if applicable). 
If an issue remains unresolved, the parties agree to document the matter in 
writing so that this Agreement and their correspondence can serve as 
contemporaneous evidence of the engagement and expenses. \textbf{The Client may 
withhold final payment} only if the \underbar{Contractor materially fails to deliver the 
agreed services and does not cure the issue within seven (7)}
\underbar{days after receiving written notice}.

\newpage
\subsection*{Parent/Guardian Acknowledgment}
The undersigned Parent/Guardian affirms that they are the legal guardian of the Contractor (a minor), have reviewed this Agreement, consent to the Contractor's participation, and agree to help ensure compliance with the obligations outlined above, including the provision of accurate tax documentation.

\vfill % Pushes the signature block to the bottom

% --- SIGNATURE BLOCK ---
\noindent IN WITNESS WHEREOF, the parties have executed this Agreement as of the Effective Date.

\vspace{2.5em}

\noindent
\begin{minipage}[t]{0.48\linewidth}
  \textbf{CLIENT}
  \vspace{2.5em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Signature
  \vspace{1.2em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Printed Name
  \vspace{1.2em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Date
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\linewidth}
  \textbf{CONTRACTOR}
  \vspace{2.5em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Signature
  \vspace{1.2em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Printed Name
  \vspace{1.2em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Date
\end{minipage}

\vspace{2.5em} % Space between rows of signatures

\noindent
\begin{minipage}[t]{0.48\linewidth}
  \textbf{CONTRACTOR GUARDIAN (Co-signer)}
  \vspace{2.5em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Signature
  \vspace{1.2em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Printed Name
  \vspace{1.2em} \\
  \rule{\linewidth}{0.4pt} \\
  \noindent Date
\end{minipage}

\end{document}
