% This is a complete LaTeX document for a Use Case Specification.
%
% Revision 6 (Full Document):
% 1. Updated author and date as requested.
% 2. Corrected 'Actors' section (Internal components removed).
% 3. Renamed external systems as 'Secondary Actors' (standard).
% 4. Added \midrule in table for readability.
% 5. Added \newpage before each Use Case.
% 6. Uses <description> list for UC metadata.
% 7. Uses high-level, non-technical language.

\documentclass{article}

% -------------------------------------------------------------------
% \ PACKAGES
% -------------------------------------------------------------------

% Encoding
\usepackage[utf8]{inputenc} % Handle UTF-8 input
\usepackage[T1]{fontenc}    % Use modern font encoding

% Language
\usepackage[english]{babel} % Set English as the primary language

% Page Layout
\usepackage[margin=1in]{geometry} % Set 1-inch margins (standard)
\usepackage{parskip}            % Use spacing between paragraphs, not indents

% Tables
\usepackage{tabularx}           % For tables that fit text width
\usepackage{booktabs}           % For professional-looking table rules (\toprule, etc.)

% Headers & Footers
\usepackage{fancyhdr}           % For custom headers and footers
\pagestyle{fancy}
\fancyhf{}                     % Clear all header and footer fields
\fancyhead[L]{System Design Documentation \textbar \ JS Law Group Website}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt} % Add a rule under the header

% Hyperlinks
\usepackage{hyperref}           % For clickable links (e.g., mailto:)
% \hypersetup{
%   colorlinks=true,
%   linkcolor=blue,
%   urlcolor=blue,
%   pdftitle={Use Case Specification: JS Law Group Website},
%   pdfauthor={Jaehoon Song}
% }

% -------------------------------------------------------------------
% \ TITLE INFORMATION
% -------------------------------------------------------------------
\title{System Design Documentation \\ \vspace*{20pt} \large JS Law Group Website}
\author{Jaehoon Song}
\date{November 14, 2025}


% -------------------------------------------------------------------
% \ DOCUMENT START
% -------------------------------------------------------------------
\begin{document}

\maketitle

\tableofcontents

\newpage

% -------------------------------------------------------------------
% \ STAKEHOLDERS
% -------------------------------------------------------------------
\section{Use Case Specification}
\subsection{Stakeholders}

\begin{tabularx}{\textwidth}{@{} p{3.2cm} X @{}}
\toprule
\textbf{Stakeholder} & \textbf{Goals and Concerns} \\
\midrule
Prospective Clients & Need fast access to practice area information, bilingual copy, proof of expertise, and an immediate way to request a consultation without sharing payment or sensitive data online. \\
\midrule % Added for readability
Family or Community Referrals & Want to scan the firm's legitimacy (team bios, testimonials, office location) on behalf of someone else. \\
\midrule % Added for readability
Attorneys and Intake Staff & Need complete, well-formatted inquiries routed to the firm's intake email so follow-ups can be triaged quickly. \\
\midrule % Added for readability
Marketing/Admin Team & Owns site content, translations, imagery, and compliance statements; cares about maintainable assets and accurate brand voice. \\
\midrule % Added for readability
Technology Operations & Maintains the website hosting and ensures all website dependencies remain reachable and secure. \\
\bottomrule
\end{tabularx}

% -------------------------------------------------------------------
% \ ACTORS
% -------------------------------------------------------------------
\subsection{Actors}

\subsubsection{Primary Actors}
\begin{itemize}
  \item \textbf{Prospective Client (English).} A person seeking legal representation who speaks English.
  \item \textbf{Prospective Client (Bilingual).} A person seeking legal representation who prefers to read in Korean, Japanese, or Spanish.
  \item \textbf{Referral or Family Member.} A person collecting information (e.g., location, contact details) on behalf of someone else.
  \item \textbf{Marketing/Admin Editor.} A firm employee responsible for maintaining website content, translations, and imagery.
\end{itemize}

\subsubsection{Secondary Actors (External Systems)}
\begin{itemize}
  \item \textbf{User's Email Application.} The client's default mail program (e.g., Outlook, Gmail, Apple Mail) that the system must interface with to send the inquiry.
  \item \textbf{Google Maps Service.} An external service that the system queries to display the interactive office map.
  \item \textbf{Third-Party Content Services.} External hosts that the system relies on to provide fonts, icons, and other design assets.
\end{itemize}




% -------------------------------------------------------------------
% \ USE CASE CATALOG
% -------------------------------------------------------------------
\newpage
\subsection{Use Case Catalog}
\subsubsection{UC-01: Select a Site Language}
\begin{description}
  \item[Primary Actor:] Prospective client (bilingual)
  \item[Secondary Actors:] User's Browser
  \item[Goal:] View all copy in a preferred language to evaluate the firm comfortably.
  \item[User Story:] As a Korean-speaking client, I want to flip the site into Korean so I can confirm services and contact steps without translation mistakes.
  \item[Preconditions:] The website has fully loaded in the default language.
  \item[Trigger:] The visitor clicks one of the language options in the navigation menu.
\end{description}
\textbf{Main Scenario:}
\begin{enumerate}
  \item The actor opens the language dropdown in the header or mobile menu.
  \item The actor selects a locale option (e.g., "Korean").
  \item The system retrieves the corresponding text and updates every label, button, and article on the page.
  \item The system saves this language choice in the user's browser, so it is remembered on future visits.
\end{enumerate}
\textbf{Alternate Flows:}
\begin{itemize}
  \item If the translation file cannot be loaded (e.g., network disruption), the system logs an error, and the website remains in the previous language.
\end{itemize}
\textbf{Postconditions:} The chosen language persists for the session. All subsequent actions and popups are shown in the selected language.

\newpage
\subsubsection{UC-02: Research Practice Areas}
\begin{description}
  \item[Primary Actor:] Prospective client (any language)
  \item[Secondary Actors:] Third-Party Content Services (for images)
  \item[Goal:] Understand whether JS Law Group covers the specific legal scenario at hand.
  \item[User Story:] As someone recovering from a collision, I want to skim the Personal Injury section and article to determine if the firm handles car and premises cases.
  \item[Preconditions:] The website is loaded.
  \item[Trigger:] The actor lands on the site or scrolls / clicks "Practice Areas".
\end{description}
\textbf{Main Scenario:}
\begin{enumerate}
  \item The actor glances at the main service cards to confirm the firm covers PI, Criminal Defense, and Family Law.
  \item The actor scrolls to the Personal Injury section, reviewing the translated bullet list of featured services.
  \item The actor reads the long-form article for deeper context.
  \item If relevant, the actor repeats the process with the Criminal Defense section.
  \item The actor navigates to About, Testimonials, or Team for further trust signals.
\end{enumerate}
\textbf{Alternate Flows:}
\begin{itemize}
  \item On mobile, the actor may use the main menu to jump directly to these sections rather than scrolling.
\end{itemize}
\textbf{Postconditions:} The actor has enough information to decide whether to contact the firm.

\newpage
\subsubsection{UC-03: Request Consultation from Main Button}
\begin{description}
  \item[Primary Actor:] Prospective client ready to contact
  \item[Secondary Actors:] User's Email Application
  \item[Goal:] Send the firm a structured inquiry that includes contact info, practice focus, and case notes.
  \item[User Story:] As a first-time visitor, I want a simple form to enter my name, phone, and case summary so the firm can call me back.
  \item[Preconditions:] The main "Get in Touch" button is visible on the screen.
  \item[Trigger:] The actor clicks "Get in Touch" in the hero.
\end{description}
\textbf{Main Scenario:}
\begin{enumerate}
  \item The contact form popup appears, showing a title and "General Inquiry" as the default topic.
  \item The actor enters first name, last name, email, optional phone, selects an inquiry type, and types a message.
  \item On submit, the system builds a formatted plain-text body with the captured data.
  \item The system opens the user's default email application with a new, pre-filled email (To: firm, Subject:, Body:) ready to be sent.
  \item The contact form popup closes and resets.
\end{enumerate}
\textbf{Alternate Flows:}
\begin{itemize}
  \item If required fields (like name or email) are missing, the form shows an error and does not submit.
  \item If the device has no email application configured, the user must use the listed phone/email manually.
\end{itemize}
\textbf{Postconditions:} The firm's intake staff receive a structured email. No sensitive information is stored on the website or in the browser.

\newpage
\subsubsection{UC-04: Launch Practice-Specific Inquiry (Mobile)}
\begin{description}
  \item[Primary Actor:] Mobile visitor with a specific case type
  \item[Secondary Actors:] User's Email Application
  \item[Goal:] Skip scrolling and open the consultation form with the correct practice type pre-selected.
  \item[User Story:] As a commuter on a phone, I want one tap to say "this is about a DUI charge" so I do not need to hunt for the correct form option.
  \item[Preconditions:] The website is viewed on a mobile device and the quick-contact button is visible.
  \item[Trigger:] The actor taps the quick-contact button and then selects "Personal Injury" or "Criminal Defense" from its menu.
\end{description}
\textbf{Main Scenario:}
\begin{enumerate}
  \item Tapping the quick-contact button reveals options for each main practice area.
  \item The actor taps one entry; the system opens the contact form and flags it with the selected topic.
  \item The contact form appears with a label (e.g., "Personal Injury") and the "Inquiry Type" dropdown is pre-filled.
  \item The actor completes the form; submission follows UC-03, steps 3-5.
\end{enumerate}
\textbf{Alternate Flows:}
\begin{itemize}
  \item If the menu is dismissed, no form opens, and the actor may use another contact method.
\end{itemize}
\textbf{Postconditions:} The resulting email clearly states the practice area, helping intake staff prioritize the inquiry.

\newpage
\subsubsection{UC-05: Locate the Office and Contact Details}
\begin{description}
  \item[Primary Actor:] Referral / family member confirming logistics
  \item[Secondary Actors:] Google Maps Service, User's Phone/Email Applications
  \item[Goal:] Obtain the office address, hours, and phone/email without opening the modal.
  \item[User Story:] As a friend helping someone schedule a visit, I want to copy the office address into my navigation app.
  \item[Preconditions:] The website is loaded.
  \item[Trigger:] The actor scrolls or navigates to the "Contact" section.
\end{description}
\textbf{Main Scenario:}
\begin{enumerate}
  \item The embedded Google Map loads the office pin.
  \item The actor reviews the address, phone, fax, and email blocks.
  \item The actor taps the phone or email link to initiate a call or compose a message using their device's native apps, or copies the address for navigation.
\end{enumerate}
\textbf{Alternate Flows:}
\begin{itemize}
  \item If the Google Maps service is blocked or fails to load, the textual address remains visible and usable.
\end{itemize}
\textbf{Postconditions:} The actor can reach out or travel to the office without using the main contact form.

\newpage
\subsubsection{UC-06: Update Localized Content}
\begin{description}
  \item[Primary Actor:] Marketing/Admin editor
  \item[Secondary Actors:] (None)
  \item[Goal:] Add or adjust copy (e.g., testimonials, partner logos, contact notices) across all supported locales in a maintainable way.
  \item[User Story:] As a content owner, I want to update the Criminal Defense article text and push it live without touching the website's code or layout.
  \item[Preconditions:] Editor has permission to edit the website's content files.
  \item[Trigger:] A change request (new testimonial, career note, or compliance statement) is approved.
\end{description}
\textbf{Main Scenario:}
\begin{enumerate}
  \item Editor updates the relevant keys in the master (English) translation file and mirrors the change in every other language file (Korean, Spanish, etc.).
  \item If imagery is involved (e.g., new partner logo), it is added to the website's image repository and referenced in the page.
  \item Editor runs a local test server to verify that translations render correctly and that contact forms still work.
  \item Changes are saved and deployed to the live website through the standard publishing workflow.
\end{enumerate}
\textbf{Alternate Flows:}
\begin{itemize}
  \item If a translation is missed for one language, the website will show the default fallback text (English) for that item.
\end{itemize}
\textbf{Postconditions:} All languages on the live website present the updated content.











\newpage
\section{Software Requirements Specification}
% -------------------------------------------------------------------
% \ INTRODUCTION
% -------------------------------------------------------------------
\subsection{Introduction}
This document captures the baseline functional and non-functional 
requirements for the JS Law Group marketing website. It serves as the 
authoritative guide for all development, quality assurance (QA), 
and future enhancement work.

\subsubsection{Scope}
The scope of this system covers the public-facing, multilingual website 
experience. This includes all content presentation (practice areas, 
attorney profiles, testimonials), the visual theme, and the client 
contact intake workflow.

Payment processing, user authentication, and internal case management systems are intentionally out of scope for this project.

% -------------------------------------------------------------------
% \ FUNCTIONAL REQUIREMENTS
% -------------------------------------------------------------------
\subsection{Functional Requirements}

\subsubsection{Site Shell and Navigation}
\begin{enumerate}
  \item \textbf{FR-01: Consistent Shell.} The system \textbf{shall} display a consistent navigation header and footer across all sections of the site.
  \item \textbf{FR-02: Fixed Navigation.} The main navigation menu \textbf{shall} remain fixed at the top of the screen. It \textbf{shall} provide links to all main content sections and \textbf{shall} collapse into a mobile-friendly menu icon on small screens.
  \item \textbf{FR-03: Theme Controls.} The system \textbf{shall} provide a control (e.g., an icon) for visitors to toggle between light and dark display modes.
  \item \textbf{FR-04: Landing Hero.} The main landing section \textbf{shall} display a translated headline, a subtitle, a primary "Get in Touch" button, and summary cards for the main practice areas (Personal Injury, Criminal Defense, Family Law).
\end{enumerate}

\subsubsection{Localized Content Delivery}
\begin{enumerate}
  \item \textbf{FR-05: Locale Management.} The system \textbf{shall} manage translations using separate data sources for each supported language (English, Korean, Japanese, Spanish). English \textbf{shall} be the default fallback language.
  \item \textbf{FR-06: Runtime Switching.} The navigation menu \textbf{shall} include a language dropdown. Selecting a language \textbf{shall} immediately translate all text on the page and \textbf{shall} save the user's choice for future visits.
  \item \textbf{FR-07: Translatable Content.} All visitor-facing text \textbf{shall} be sourced from the central translation files. This includes articles, labels, buttons, and form fields.
  \item \textbf{FR-08: State Refresh.} The system \textbf{shall} refresh its state when the browser tab regains focus, ensuring the most recent content and settings are displayed.
\end{enumerate}

\subsubsection{Practice Content and Social Proof}
\begin{enumerate}
  \item \textbf{FR-09: Practice Detail Sections.} The site \textbf{shall} feature dedicated sections for Personal Injury and Criminal Defense, showing relevant imagery, bulleted lists of services, and long-form descriptive articles.
  \item \textbf{FR-10: Attorney Profiles.} The site \textbf{shall} display attorney profiles, including name, title, biography, and a professional photo.
  \item \textbf{FR-11: Testimonials and Partners.} The system \textbf{shall} display a carousel of client testimonial quotes and a grid of partner firm logos.
  \item \textbf{FR-12: Team Profiles.} The "Team" section \textbf{shall} render profiles for team members, including their photo, role, and contact method, sourced from a central data file.
  \item \textbf{FR-13: Careers Messaging.} A careers section \textbf{shall} communicate hiring values and provide a contact method for applications.
\end{enumerate}

\subsubsection{Engagement and Intake}
\begin{enumerate}
  \item \textbf{FR-14: CTA Context.} All "Contact" and "Get in Touch" buttons \textbf{shall} open the same consultation contact form. The form \textbf{shall} be aware of which button was clicked (e.g., "Personal Injury" vs. "General").
  \item \textbf{FR-15: Contact Modal.} The consultation contact form \textbf{shall} appear as a popup (modal). It \textbf{shall} collect the visitor's first name, last name, email, phone, inquiry type, and a message.
  \item \textbf{FR-16: Mail Client Handoff.} Upon submission, the system \textbf{shall} prepare a pre-formatted email and open the visitor's default mail application to send the inquiry to the firm. No visitor data \textbf{shall} be stored on the server.
  \item \textbf{FR-17: Floating Action Button.} A "Floating Action Button" (FAB) \textbf{shall} be visible on mobile, providing shortcuts to request a consultation for specific practice areas.
  \item \textbf{FR-18: Contact Information Section.} The "Contact" section \textbf{shall} display an embedded, interactive Google Map of the office. It \textbf{shall} also list the firm's address, contact details, and hours, using icons for readability.
  \item \textbf{FR-19: Social Links.} The footer \textbf{shall} provide links to the firm's verified social media profiles and static policy pages.
\end{enumerate}

% -------------------------------------------------------------------
% \ NON-FUNCTIONAL REQUIREMENTS
% -------------------------------------------------------------------
\subsection{Non-Functional Requirements}
\begin{enumerate}
  \item \textbf{NFR-01: Responsive Layout.} The website layout \textbf{shall} be fully responsive, adapting cleanly to desktop, tablet, and mobile screen sizes without horizontal scrolling.
  \item \textbf{NFR-02: Accessibility.} The website \textbf{shall} adhere to Web Content Accessibility Guidelines (WCAG) AA standards. This includes use of semantic HTML, alt text for images, and full keyboard navigation support.
  \item \textbf{NFR-03: Performance.} The website \textbf{shall} load quickly. External resources (fonts, icons) \textbf{shall} be loaded from a Content Delivery Network (CDN). The 'Largest Contentful Paint' (LCP) \textbf{shall} be under 2.5 seconds on a standard broadband connection.
  \item \textbf{NFR-04: Privacy and Security.} No Personally Identifiable Information (PII) \textbf{shall} be transmitted to or stored by the website's server. The system \textbf{shall} only use local browser storage for theme and language preferences. A privacy statement \textbf{shall} be included in the footer.
  \item \textbf{NFR-05: Localization Quality.} When new content is added, corresponding translations \textbf{shall} be added for all supported languages to avoid displaying fallback (English) text.
  \item \textbf{NFR-06: Maintainability.} All new code \textbf{shall} be modular, separated from content, and well-documented to ensure future maintainability.
  \item \textbf{NFR-07: Availability.} The website \textbf{shall} be built as a 'static site' and be hostable on any standard web server without requiring server-side processing.
  \item \textbf{NFR-08: Browser Support.} The system \textbf{shall} be fully functional on the two most recent versions of Chrome, Safari, Edge, and Firefox on both desktop and mobile platforms.
\end{enumerate}

% -------------------------------------------------------------------
% \ DEPENDENCIES AND CONSTRAINTS
% -------------------------------------------------------------------
\subsection{Dependencies and Constraints}
\begin{itemize}
  \item The system \textbf{is constrained} to use the Bootstrap 5 framework.
  \item The system \textbf{is constrained} to use the Font Awesome 6 icon library.
  \item The system \textbf{is dependent} on the Google Fonts service for typography.
  \item The map feature \textbf{is dependent} on the Google Maps embedding service and requires an active internet connection.
  \item The contact workflow \textbf{is dependent} on the visitor having a correctly configured email client on their device.
  \item The system \textbf{is dependent} on the user's browser supporting LocalStorage for persisting language and theme preferences.
\end{itemize}







\end{document}